A meta analysis of tournaments and an evaluation of performance in the Iterated Prisoner's Dilemma.

### 2019-12-29 paper/main.tex
fixes re writes.
This was meant to be 3 different commits but I forgot to commit.
The re writes are the following:

- Conclusion in noisy tourmanets. Explain better that the highly ranked
strategies did so because of their performance in tournaments with p>0.5
- Final conclusion of top rank strategies section. Tweaked the text
a little bit
- Better explanation regarding the clustering of the performances.
The different approaches are now bullet points.

The result summary, Table~\ref{table:output_result}, has \(N\) number of rows
because each row contains information for each strategy that participated in the
tournament. The information includes the strategy's rank, median score, the rate
with which the strategy cooperated $(C_r)$, its match win count and the
probability that the strategy cooperated in the opening move. Moreover, the
probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
and the rate of which the strategy cooperated after each state. A feature that
has been manually included is the \textbf{normalised rank}. The rank of a given
strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
denoted as $r$, is calculated as a strategy's rank divided by the tournament's
size $N$ minus 1. In the next section the performance of these strategies is evaluated
based on their normalised rank.

>>>>

The result summary, Table~\ref{table:output_result}, has \(N\) rows
because each row contains information for each strategy that participated in the
tournament. The information includes the strategy's rank, median score, the rate
with which the strategy cooperated $(C_r)$, its match win count and the
probability that the strategy cooperated in the opening move. Moreover, the
probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
and the rate of which the strategy cooperated after each state. A feature that
has been manually included is the \textbf{normalised rank}. The rank of a given
strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
denoted as $r$, is calculated as a strategy's rank divided by the tournament's
size $N$ minus 1. In the next section the performance of these strategies is evaluated
based on their normalised rank.
